Co-citations in context

### 2019-06-13 cocit_r.tex
Minor revisions

 We tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary subnetwork.  The results (Table \ref{tab:kld}) confirm this prediction: simulations under the constrained model (which constrains substitutions to the
disciplinary subnetwork) consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable. Furthermore, the K-L divergence for  the unconstrained model is generally twice as large as the K-L divergence for the models where the references are constrained to  the disciplinary subnetworks (a ratio of 1.96 to 2.77,  and  greater than 2.0 for eight out of nine cases).
These results clearly demonstrate that constraining reference substitutions to the given disciplinary network better models the observed data.

>>>>

 We tested the conjecture that model misspecification would be reduced by constraining the substitutions to  disciplinary subnetworks by examining the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and predicted citation distributions, restricted to  the set of journals in a given disciplinary subnetwork.  The results (Table \ref{tab:kld}) confirm this prediction: simulations \textcolor{blue}{under the constrained model (which constrains substitutions to the
disciplinary subnetwork)} consistently have a lower K-L divergence compared to simulations under the unconstrained model,  where all references in WoS for a given year are equiprobable. Furthermore, the K-L divergence for  the unconstrained model is generally twice as large as the K-L divergence for the models where the references are constrained to  the disciplinary subnetworks (ratios range from 1.96 to 2.77,  and are greater than 2.0 in eight out of nine cases).
These results clearly demonstrate that constraining reference substitutions to the given disciplinary network better models the observed data.
